\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2015-01-28 doc/sw-system.tex
Simplified timing analysis section draft to focus on rate plot, as in #95

@@

@@

\item Integrated humanpower = X (stage 1) and y (stage 2), cf hours taken by
small team of experts

>>>>

\subsection{Classification Speed}
\label{sec:results:speed}

% How fast does the \sw crowd classify subjects? Each agent records the
% timestamp of each classification its volunteer makes; by measuring the time
% lags between successive classifications we can make estimates of each
% volunteer's speed, and that of the crowd.
% 
% A histogram of all time lags for all volunteers is shown in
% \Fref{fig:crowd:timelags}, with those of the ``experienced volunteers''
% (those who classified 10 or more training subjects.) overlaid. 
% 
% \todo{PJM}{Make this histogram, and try and infer the typical inter-session
% lag.}
% 
% Defining a new classification session to have started at least X minutes since
% the previous classification, we assign all classifications into sessions, and
% compute the mean intra-session time lag recorded by each agent. This gives
% some measure of classification speed within a session; we also compute the 
% mean session length, and the rate of information contribution. The
% latter is the most relevant measure of speed for future project design. The
% distributions of these speeds are shown in \Fref{fig:crowd:speeddists}, in a corner
% plot that also shows the effort and skill from \Fref{fig:crowd:cornerplot}. We
% see that ...

The overall contribution rate for the \sw crowd was found,
and is plotted as a function of time in \Fref{fig:crowd:speed}. We see that
...

\todo{Phil, Chris}{Compute classification speeds, make plots, discuss. \#95}

@@

% Questions we set ourselves in the introduction:
% \begin{itemize}
% \item How reliably can we find gravitational lenses using the \sw
% system? What is the completeness of the sample produced likely to be?
% \item How noisy is the system? What is the purity of the sample
% produced?
% \item How quickly can lenses be detected, and non-lenses be rejected?
% How many classifications, and so how many volunteers are needed per target?
% \item What can we learn about the scalability of the crowd-sourcing approach?
% \end{itemize}

@@

\item Integrated humanpower = X (stage 1) and Y (stage 2), cf hours taken by
small team of experts
